Efficient Handling of String-Number Conversion

### 2020-03-31 final-version/evaluation.tex
update of numbers in the experiments text, removal the story about most failures of Z3-Trau due to the one function.

From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools. It fails on twice less cases then Z3, which is ranked the 2nd. In fact, most of the failed tests come from the analysis of one Python core library function that converts an IPv6 address to a number. From around 2028 tests generated from this function, around 1000 tests are too difficult for all solvers.  If we exclude the 2028 tests generated from this function, then {\tool} has only $218$ failed cases in total. This is significantly better than the 2nd place tool Z3, which fails on $942$ cases in total.

>>>>

\changed{
From Table~\ref{table:str_int_benchmark}, we can see that {\tool} significantly outperforms all other tools. 
The second best tool, Z3, fails on 38\% more examples. 
}
%It fails on twice less cases then Z3, which is ranked the 2nd. In fact, most of the failed tests come from the analysis of one Python core library function that converts an IPv6 address to a number. From around 2028 tests generated from this function, around 1000 tests are too difficult for all solvers.  If we exclude the 2028 tests generated from this function, then {\tool} has only $218$ failed cases in total. This is significantly better than the 2nd place tool Z3, which fails on $942$ cases in total.
